Regression Analysis—Interactions

### 2019-03-28 figures/gatekeeper_representation/gatekeeper_representation.rmd
updates to figures and labels—prepreparing for re-submission

# setup theme
theme_dakota <- function () { 
    theme_bw(base_size=10, base_family="Times") %+replace% 
        theme(
            strip.background = element_blank(),
            strip.text = element_text(face = "bold"),
            plot.title = element_text(size = 11, face = "bold"),
            axis.text.x = element_text(size = 9, margin = margin(t = 5, b = 5)),
            legend.title = element_blank(),
            legend.position = "bottom"
        )
}

@@

### Load the required data
```{r message=FALSE, warning=FALSE}
people <- read_csv("https://www.dropbox.com/s/ic2b17xp3wo0255/elife_people.csv?dl=1")
head(people)
```

@@

sig_df <- data.frame(type = rep(c("Gatekeeper", "Corr. Author", "First Author", "Last Author"), 1), 
                     gender = rep(c("Male", "Female"), 2),  
                     sig = c("N/A", sig2ast(corr$p.value), sig2ast(first$p.value), sig2ast(last$p.value)))

gender_sig_list <- list("Corresponding Author" = corr, "First Author" = first, "Last Author" = last)

expected <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  filter(type == "Gatekeeper") %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    expected_prop = n() / total[1]
  ) %>%
  ungroup() %>%
  select(-type)

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("gender", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 1.5, y = 0.9)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right",
    plot.title = element_text(size = 18)
  ) +
  labs(y = "Proportion",
       title = "A") +
  guides(fill = F)

@@

sig_df <- data.frame(type = rep(c("Gatekeeper", "Corr. Author", "First Author", "Last Author"), 3), 
                     continent = rep(c("Africa", "Asia", "Europe", "North America", "Oceania", "South America"), 2),  
                     sig = c("N/A", sig2ast(corr$p.value), sig2ast(first$p.value), sig2ast(last$p.value)))

continent_sig_list <- list("Corresponding Author" = corr, "First Author" = first, "Last Author" = last)

# Now we should repeat this graph, except this time for the continental representation
expected <- people %>%
  filter(type == "Gatekeeper") %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    expected_prop = n() / total[1]
  ) %>%
  ungroup() %>%
  select(-type)

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("continent", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    continent = reorder(continent, -prop),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 3.5, y = 0.92)) +
  geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank(),
    plot.title = element_text(size = 18)
  ) +
  labs(y = "Proportion",
       title = "B") +
  scale_fill_brewer(palette = "Set2")

@@

And below are the explicit results of the significaince tests used in the previous graphs to compare the actual proportion of male/female authors with the expected proportion given the population of gatekeepers. 
```{r}
fig3_top_sig_table <- data.frame(
  authorship = c("Corresponding", "First", "Last"),
  p.value = sapply(gender_sig_list, function(x) x$p.value),
  n = sapply(gender_sig_list, function(x) sum(x$observed)),
  statistic = sapply(gender_sig_list, function(x) x$statistic),
  df = sapply(gender_sig_list, function(x) x$parameter)
)

@@

And the same for the continent-level tests
```{r}
fig3_bottom_sig_table <- data.frame(
  continent = c("Corresponding", "First", "Last"),
  p.value = sapply(continent_sig_list, function(x) x$p.value),
  n = sapply(continent_sig_list, function(x) sum(x$observed)),
  statistic = sapply(continent_sig_list, function(x) x$statistic),
  df = sapply(continent_sig_list, function(x) x$parameter)
)

@@

stargazer(gender_dem, summary = F, rownames = F, type = "latex", font.size = "scriptsize")

```

>>>>

# setup theme
theme_dakota <- function () { 
    theme_bw(base_size=10, base_family="Times") %+replace% 
        theme(
            strip.background = element_blank(),
            strip.text = element_text(size = 12),
            plot.title = element_text(size = 18, face = "bold"),
            axis.text.x = element_text(size = 9, margin = margin(t = 5, b = 5), face = "bold"),
            legend.title = element_blank(),
            legend.position = "bottom"
        )
}

@@

### Load the required data
```{r message=FALSE, warning=FALSE}
people <- read_csv("https://www.dropbox.com/s/ic2b17xp3wo0255/elife_people.csv?dl=1") %>%
  select(-X1)

# Need to use the non-anonymous data here
elife <- read.csv("https://www.dropbox.com/s/dmvmzz57m7t4xtq/non_anonymous_data.csv?dl=1")

ca_full_sub <- subset(elife, has_full_submission) %>%
  group_by(ca_name) %>%
  slice(1) %>%
  ungroup() %>%
  select(ca_gender, ca_continent) %>%
  rename(gender = ca_gender, continent = ca_continent) %>%
  mutate(type = "Corr.Full")

people <- rbind(people, ca_full_sub) %>%
  filter(continent != "Antarctica")

head(people)
```

@@

s <- subset(people, type == "Corr.Full" | type == "Gatekeeper" )
t <- t(table(s$gender, s$type))
corr.full <- chisq.test(t[2, 1:2], p = prop.table(t[1, 1:2]))

sig_df <- data.frame(type = rep(c("Gatekeeper", "Corr. Author", "First Author", "Last Author", "Corr.Full"), 1), 
                     #gender = rep(c("Male", "Female"), 2),  
                     sig = c("N/A", sig2ast(corr$p.value), sig2ast(first$p.value), sig2ast(last$p.value), sig2ast(corr.full$p.value)))

gender_sig_list <- list("Corresponding Author" = corr, "First Author" = first, "Last Author" = last, "Corr.Full" = corr.full)

expected <- people %>%
  filter(gender %in% c("M", "F")) %>%
  filter(type != "Corr.Full") %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  filter(type == "Gatekeeper") %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    expected_prop = n() / total[1] * 100
  ) %>%
  ungroup() %>%
  select(-type)

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1] * 100
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", 
                             "Corr. Author",
                             "First Author",
                             "Corr.Full",  
                             "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", 
                             "Corr. Author" = "Corresponding (Initial)", 
                             "First Author" = "First", 
                             "Corr.Full" = "Corresponding (Full)",
                             "Last Author" = "Last")),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  #geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 1.5, y = 92)) +
  #geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 85, 101), yend = ifelse(sig != "N/A", 85, 101)), color = "black") +
  facet_wrap(~type, nrow = 1, labeller = labeller(type = label_wrap_gen(10))) +
  theme_dakota() +
  ylim(c(0, 100)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right"
  ) +
  labs(y = "",
       title = "A") +
  guides(fill = F)

@@

s <- subset(people, continent != "Antarctica" & (type == "Corr.Full" | type == "Gatekeeper" ))
t <- t(table(s$continent, s$type))
corr.full <- chisq.test(t[2, ], p = prop.table(t[1, ]))

sig_df <- data.frame(type = rep(c("Gatekeeper", "Corr. Author", "First Author", "Last Author", "Corr.Full"), 1), 
                     #continent = rep(c("Africa", "Asia", "Europe", "North America", "Oceania", "South America"), 2),  
                     sig = c("N/A", sig2ast(corr$p.value), sig2ast(first$p.value), sig2ast(last$p.value), sig2ast(corr.full$p.value)))

continent_sig_list <- list("Corresponding Author" = corr, "First Author" = first, "Last Author" = last, "Corr.Full" = corr.full)

# Now we should repeat this graph, except this time for the continental representation
expected <- people %>%
  filter(type == "Gatekeeper") %>%
  mutate(total = n()) %>%
  group_by(type, continent) %>%
  summarize(
    expected_prop = n() / total[1] * 100
  ) %>%
  ungroup() %>%
  select(-type)

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1] * 100
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", 
                             "Corr. Author", 
                             "First Author", 
                             "Corr.Full",  
                             "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", 
                             "Corr. Author" = "Corresponding (Initial)", 
                             "First Author" = "First",
                             "Corr.Full" = "Corresponding (Full)",
                             "Last Author" = "Last")),
    continent = reorder(continent, -prop),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "longdash") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  #geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 3.5, y = 92)) +
  #geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 85, 101), yend = ifelse(sig != "N/A", 85, 101)), color = "black") +
  facet_wrap(~type, nrow = 1, labeller = labeller(type = label_wrap_gen(10))) +
  theme_dakota() +
  ylim(c(0, 100)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank()
  ) +
  labs(y = "",
       title = "B") +
  scale_fill_brewer(palette = "Set2")

@@

And below are the explicit results of the significaince tests used in the previous graphs to compare the actual proportion of male/female authors with the expected proportion given the population of gatekeepers. 
```{r}
fig3_top_sig_table <- data.frame(
  authorship = c("Corresponding", "First", "Last", "Corr.Full"),
  p.value = sapply(gender_sig_list, function(x) x$p.value),
  n = sapply(gender_sig_list, function(x) sum(x$observed)),
  statistic = sapply(gender_sig_list, function(x) x$statistic),
  df = sapply(gender_sig_list, function(x) x$parameter)
)

@@

And the same for the continent-level tests
```{r}
fig3_bottom_sig_table <- data.frame(
  continent = c("Corresponding", "First", "Last", "Corr.Full"),
  p.value = sapply(continent_sig_list, function(x) x$p.value),
  n = sapply(continent_sig_list, function(x) sum(x$observed)),
  statistic = sapply(continent_sig_list, function(x) x$statistic),
  df = sapply(continent_sig_list, function(x) x$parameter)
)

@@

stargazer(gender_dem, summary = F, rownames = F, type = "latex", font.size = "scriptsize")
```

### 2019-03-28 figures/regression_analysis/regression_analysis_interaction.rmd
updates to figures and labels—prepreparing for re-submission

```{r message=FALSE, warning=FALSE}
# Load required packages
library(tidyverse)
library(lmtest)
library(tidyr)
library(stargazer)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(grid)
library(gridExtra)
```

@@

elife$submission_year <- elife$submission_year - 2012
dim(elife)
```

@@

### Construct a regression table for the 
```{r}
initial.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America",
               "I(ca_se_dist/1e+06)" = "Geographic distance (1000s km)",
               "ca_se_dist_zeroTRUE" = "Geographic distance is zero"
               )

@@

### Construct the initial regression plot
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "A. Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

initial_reg_plot
```

@@

### Run ANOVA on the model...
```{r}
anova(full_model, test = "Chisq")
```

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geo. distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geo. distance is zero",
               "author_reviewer_interactionFemale Author, All Women" = "Last author female - all rev. female",
               "author_reviewer_interactionFemale Author, Mixed" = "Last author female - mixed rev.",
               "author_reviewer_interactionMale Author, All Men" = "Last author male - all rev. male",
               "author_reviewer_interactionMale Author, All Women" = "Last author male - all rev. female",
               "author_reviewer_interactionMale Author, Mixed" = "Last author male - mixed rev."
               )

stargazer(full_model, 
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = full.cov.labels, 
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/full_model.txt", append=F)
#out

@@

```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           rm.terms = c("fa_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .4, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "B. Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

full_reg_plot
```

### Arrange the plots
```{r}
regressions_interactions <- grid.arrange(initial_reg_plot, full_reg_plot, ncol = 2)
```

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_interactions, height = 8, width = 10)
```

>>>>

```{r message=FALSE, warning=FALSE}
# Load required packages
library(tidyverse)
library(lmtest)
library(tidyr)
library(stargazer)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(grid)
library(gridExtra)
library(broom)

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "***", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}
```

@@

elife$submission_year <- elife$submission_year-2012
dim(elife)
```

@@

### Construct a regression table for the 
```{r}
initial.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. Author from Africa",
               "ca_continentAsia" = "Corr. Author from Asia",
               "ca_continentEurope" = "Corr. Author from Europe",
               "ca_continentOceania" = "Corr. Author from Oceania",
               "ca_continentSouth America" = "Corr. Author from South America",
               "I(ca_se_dist/1e+06)" = "Corr. Author-Editor Geo. Distance",
               "ca_se_dist_zeroTRUE" = "Corr. Author-Editor Geo. Distance = 0"
               )

@@

@@

```{r}
main_effects <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_gender + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero + composition, data = subset(full_with_inter, included), family = "binomial")
summary(main_effects)
```

```{r}
standard_interaction <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_gender + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero + composition + la_gender:composition, data = subset(full_with_inter, included), family = "binomial")
summary(standard_interaction)
```

### Run ANOVA on the model...
```{r}
anova(standard_interaction, test = "Chisq")
```

Mixed-gender only
```{r}
mixed <- glm(accepted ~ submission_year + submission_type + fa_gender +  la_institution_rank + la_gender + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero, data = subset(full_with_inter, included & composition == "Mixed"), family = "binomial")
summary(mixed)
```

All-Male
```{r}
all_male <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_gender + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero, data = subset(full_with_inter, included & composition == "All Men"), family = "binomial")
summary(all_male)
```

```{r}
main_effects_tidy <- tidy(main_effects, conf.int = T, exponentiate = T) %>%
  mutate(type = "Main Effects")
standard_interaction_tidy <- tidy(standard_interaction, conf.int = T, exponentiate = T) %>%
  mutate(type = "With Interaction")
mixed_only_tidy <- tidy(mixed, conf.int = T, exponentiate = T) %>%
  mutate(type = "Mixed Reviewers Only")
all_male_only_tidy <- tidy(all_male, conf.int = T, exponentiate = T) %>%
  mutate(type = "All-Male Reviewers Only")
global_tidy <- tidy(full_model, conf.int = T, exponentiate = T) %>%
  mutate(type = "Global Interactions")

all_models <- rbind(main_effects_tidy,
      standard_interaction_tidy,
      mixed_only_tidy,
      all_male_only_tidy,
      global_tidy)
```

```{r}
full.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "compositionAll Men" = "All Male Rev.",
               "compositionAll Women" = "All Female Rev.",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author is Male",
               "la_continentAfrica" = "Last Author from Africa",
               "la_continentAsia" = "Last Author from Asia",
               "la_continentEurope" = "Last Author from Europe",
               "la_continentOceania" = "Last Author from Oceania",
               "la_continentSouth America" = "Last Author from South America",
               "I(la_reviewer_dist/1e+06)" = "Last Author-Reviewers Geo. Distance",
               "la_reviewer_dist_zeroTRUE" = "Last Author-Reviewers Geo. Distance = 0",
               "la_genderM:compositionAll Men" = "Last Author Male*All Male Rev.",
               "la_genderM:compositionAll Women" = "Last Author Male*All Women Rev.",
               "author_reviewer_interactionFemale Author, All Women" = "Last Author Female-All Female Rev.",
               "author_reviewer_interactionFemale Author, Mixed" = "Last Author Female-Mixed Rev.",
               "author_reviewer_interactionMale Author, All Men" = "Last Author Male-All Male Rev.",
               "author_reviewer_interactionMale Author, All Women" = "Last Author Male-All Female Rev.",
               "author_reviewer_interactionMale Author, Mixed" = "Last Author Male-Mixed Rev."
               )

both.full.plots <- all_models %>%
  filter(type == "Global Interactions" | type == "Main Effects") %>%
  filter(term != "(Intercept)") %>%
  mutate(
    type = factor(type, 
                  levels = c("Main Effects", "Global Interactions"),
                  labels = c("A. Main Effects", "B. Global Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  facet_grid(~type) +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast))),
            vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18)) +
  geom_hline(yintercept = 1, color = "black") +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        strip.text = element_text(size = 12, face = "bold"),
        axis.text.y = element_text(size = 11)) +
  labs(y = "Odds Ratio")

both.full.plots
```

### Construct the plot for full submissions
```{r}
full.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "compositionAll Men" = "All Male Rev.",
               "compositionAll Women" = "All Female Rev.",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author is Male",
               "la_continentAfrica" = "Last Author from Africa",
               "la_continentAsia" = "Last Author from Asia",
               "la_continentEurope" = "Last Author from Europe",
               "la_continentOceania" = "Last Author from Oceania",
               "la_continentSouth America" = "Last Author from South America",
               "I(la_reviewer_dist/1e+06)" = "Last Author-Reviewers Geo. Distance",
               "la_reviewer_dist_zeroTRUE" = "Last Author-Reviewers Geo. Distance = 0",
               "author_reviewer_interactionFemale Author, All Women" = "Last Author Female-All Female Rev.",
               "author_reviewer_interactionFemale Author, Mixed" = "Last Author Female-Mixed Rev.",
               "author_reviewer_interactionMale Author, All Men" = "Last Author Male-All Male Rev.",
               "author_reviewer_interactionMale Author, All Women" = "Last Author Male-All Female Rev.",
               "author_reviewer_interactionMale Author, Mixed" = "Last Author Male-Mixed Rev."
               )

stargazer(full_model, 
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = full.cov.labels,
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )
```

```{r}
main.effects.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author is Male",
               "la_continentAfrica" = "Last Author from Africa",
               "la_continentAsia" = "Last Author from Asia",
               "la_continentEurope" = "Last Author from Europe",
               "la_continentOceania" = "Last Author from Oceania",
               "la_continentSouth America" = "Last Author from South America",
               "I(la_reviewer_dist/1e+06)" = "Last Author-Reviewers Geo. Distance",
               "la_reviewer_dist_zeroTRUE" = "Last Author-Reviewers Geo. Distance = 0",
               "compositionAll Men" = "All Male Rev.",
               "compositionAll Women" = "All Female Rev."
               )

stargazer(main_effects, 
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = main.effects.cov.labels,
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )
```

```{r}
summary(standard_interaction)

@@

```{r}

all.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author is Male",
               "la_continentAfrica" = "Last Author from Africa",
               "la_continentAsia" = "Last Author from Asia",
               "la_continentEurope" = "Last Author from Europe",
               "la_continentOceania" = "Last Author from Oceania",
               "la_continentSouth America" = "Last Author from South America",
               "I(la_reviewer_dist/1e+06)" = "Last Author-Reviewers Geo. Distance",
               "la_reviewer_dist_zeroTRUE" = "Last Author-Reviewers Geo. Distance = 0",
               "compositionAll Men" = "All Male Rev.",
               "compositionAll Women" = "All Female Rev.",
               "la_genderM:compositionAll Men" = "Last Author Male*All Male Rev.",
               "la_genderM:compositionAll Women" = "Last Author Male*All Women Rev.",
               "author_reviewer_interactionFemale Author, All Women" = "Last Author Female-All Female Rev.",
               "author_reviewer_interactionFemale Author, Mixed" = "Last Author Female-Mixed Rev.",
               "author_reviewer_interactionMale Author, All Men" = "Last Author Male-All Male Rev.",
               "author_reviewer_interactionMale Author, All Women" = "Last Author Male-All Female Rev.",
               "author_reviewer_interactionMale Author, Mixed" = "Last Author Male-Mixed Rev."
               )

stargazer(main_effects, standard_interaction, all_male, mixed, full_model,
          type = "latex",
          style = "ajs",
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          column.labels = c("Main Effects", "With interaction", "Only All-Male", "Only Mixed", "Global Interaction"),
          covariate.labels = all.cov.labels)

```{r}
interaction.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author Male",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geo. distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geo. distance is zero",
               "compositionAll Men" = "All Reviewers Male",
               "compositionAll Women" = "All Reviewers Women",
               "la_genderM:compositionAll Men" = "Last Author Male*All Reviewers Male",
               "la_genderM:compositionAll Women" = "Last Author Male*All Reviewers Female"
               )

stargazer(standard_interaction, 
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = interaction.cov.labels,
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )
```

```{r}
interaction.anova.labels = c(
               "submission_year" = "Submission Year", 
               "submission_type" = "Submission Type", 
               "fa_gender" = "First Author Gender",
               "la_institution_rank" = "Last Author Inst. Prestige",
               "la_gender" = "Last Author Gender",
               "la_continent" = "Last author Continent",
               "I(la_reviewer_dist/1e+06)" = "Last Author-Reviewers Geographic Distance",
               "la_reviewer_dist_zero" = "Sum of geo. distance is zero",
               "composition" = "Reviewer Gender Composition",
               "la_gender:composition" = "Last Author Gender*Reviewer Gender Composition"
               )

anova.table <- anova(standard_interaction, test = "Chisq")
anova.tidy <- tidy(anova.table) %>%
  filter(term != "NULL") %>%
  mutate(term = factor(term),
         term = plyr::revalue(term, interaction.anova.labels),
         term = as.character(term),
         Deviance = round(Deviance, 3),
         Resid..Df = round(Resid..Df, 3),
         Resid..Dev = round(Resid..Dev, 3),
         p.value = round(p.value, 5))

anova.tidy

stargazer(anova.tidy,
          summary = FALSE,
          column.labels = c("Term", "df", "Deviance", "Resid. Df", "Resid. Deviance", "P-value"),
          type = "latex")
```

```{r}
main.effects.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_genderM" = "Last Author Male",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geo. distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geo. distance is zero",
               "compositionAll Men" = "All Reviewers Male",
               "compositionAll Women" = "All Reviewers Women"
               )

stargazer(all_male, mixed, 
          column.labels = c("All Male", "Mixed-Gender"),
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = main.effects.cov.labels,
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.full.plots, height = 8, width = 10)
```
